Meta analysis of differential expression results from AMP-AD (Control vs AD, reprocessed RNASeq)

### 2017-05-17 code/Rmd/MetaAnalysis.Rmd
metananlysis temp commit

library(Vennerable)
library(colorfulVennPlot)

@@

# Download AD genetic loci from synapse
AD = list(GeneticLoci = synGet('syn4891675')@filePath %>%
            read.table(header = F) %>% 
            unlist() %>%
            as.character())

list()
GL_OBJ = synGet('syn4893059');
ALL_USED_IDs = c(ALL_USED_IDs, GL_OBJ$properties$id)
load(GL_OBJ@filePath)

GeneSets.CM = list(CellTypeMarkers = GeneSets[grep('Zhang', names(GeneSets))],
                   AD = GeneSets['AD:GeneticLoci'])
GeneSets = c(GeneSets.Enrichr, GeneSets.CM) # 
```

>>>>

library(Vennerable)
library(colorfulVennPlot)
library(xlsx)

@@

# Download AD genetic loci from synapse
AD = list(GeneticLoci = synGet('syn4891675')@filePath %>%
            read.table(header = F) %>% 
            unlist() %>%
            as.character())
all.used.ids = c(all.used.ids, 'syn4891675')

# Download cell type markers from synapse (list from GSE73721 by Mariet)
load(synGet('syn9818080')@filePath)
all.used.ids = c(all.used.ids, 'syn9818080')

GeneSets = c(list(CellTypeMarkers = CellTypeList,
                AD = AD),
                GeneSets.Enrichr)
```
